Translation of B Implementations to the LLVM: Control and Modularity

### 2013-08-28 translation.tex
Added a B implementation example to validate the translation of WHILE instructions. Added a LLVM scaffolding to instantiate the B implementation and call its operations. Implemented the translation for WHILE instructions. Created a Python module to ease constructing the representation of the abstract syntax trees of B implementation. Updated the definition of the translation to reflect necessary corrections. Updated the contents of the README file and removed useless files from the PROTO directory.

\paragraph{Predicates}
The translation of conditions takes as input a condition node \B{n}, as well as
two labels $\ell_t$ and $\ell_f$ that correspond to program locations where the
execution shall jump when the condition is evaluted to true or false,
respectively.  The first rule defines the translation of an atomic relation:
\begin{align*}
  \lefteqn{\trad{n, $\ell_t$, $\ell_f$}{\B{Form}} \isdef
  \textbf{ let } p \sep v = \trad{n}{\B{Comp}} \IN} \\
  & \llvm{"\PH{p} \quad br i1 \PH{v}, label \PH{\ell_t}, label \PH{\ell_f} \nl"}
\end{align*}

@@

\paragraph{While instructions} are translated in two blocks of instructions:
block $\ell_1$ evaluates the loop condition and block $\ell_2$ executes the loop
body:
\begin{align*}
\begin{split}
\trad{w, $\ell$}{\B{While}} \isdef 
  & \LET \ell_1 = \lbl \AND \ell_2 = \lbl \AND c \sep v = \trad{w.cond}{\B{Pred}} \IN \\
  & \llvm{"\PH{\ell_1} : \PH{c}} \\
  & \llvm{br i1 \PH{v}, label \PH{\ell_2}, label \PH{\ell} \nl} \\
  & \llvm{\PH{\ell_2} : \PH{\trad{i.body, $\ell_1$}{\ListOf{\B{Inst}}}_L}}
\end{split}
\end{align*}

@@

\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|}
\hline
Example nº & 01 & 02 \\
\hline
variables & \yes & \yes \\
constants & \no & \yes \\
op. input & \yes & \no \\
op. output & \yes & \no \\
\hline
\multicolumn{3}{|c|}{instructions} \\
\hline
block & \yes & \no \\
local var & \no & \no \\
identity & \no & \no \\
becomes equal & \yes & \yes \\
operation call & \no & \no \\
condition & \yes & \no \\
case & \no & \no \\
assertion & \no & \no \\
sequence & \yes & \yes \\
while & \no & \no \\
\hline
\multicolumn{3}{|c|}{expressions} \\
\hline
succ & \no & \yes \\
pred & \no & \yes \\
+ & \yes & \no \\
- & \yes & \no \\
\hline
\multicolumn{3}{|c|}{formulas} \\
\hline
and & \no & \no \\
or & \no & \no \\
not & \no & \no \\
comparison & \yes & \yes \\
\hline
\end{tabular}
\end{center}

>>>>

\paragraph{Predicates}
The translation of conditions takes as input a condition node \B{n}, as well as
two labels $\ell_t$ and $\ell_f$ that correspond to program locations where the
execution shall jump when the condition is evaluted to true or false,
respectively.  The first rule defines the translation of an atomic relation:
\begin{align*}
  \lefteqn{\trad{n, $\ell_t$, $\ell_f$}{\B{Form}} \isdef
  \textbf{ let } p \sep v = \trad{n}{\B{Comp}} \IN} \\
  & \llvm{"\PH{p} \quad br i1 \PH{v}, label \%\PH{\ell_t}, label \%\PH{\ell_f} \nl"}
\end{align*}

@@

\paragraph{While instructions} are translated in two blocks of instructions:
block $\ell_1$ evaluates the loop condition and block $\ell_2$ executes the loop
body:
\begin{align*}
\begin{split}
\trad{w, $\ell$}{\B{While}} \isdef 
  & \LET \ell_1 = \lbl \AND \ell_2 = \lbl \AND c \sep v = \trad{w.cond}{\B{Pred}} \IN \\
  & \llvm{"br label \%\PH{\ell_1} \nl} \\
  & \llvm{\PH{\ell_1} : \PH{c}} \\
  & \llvm{br i1 \PH{v}, label \%\PH{\ell_2}, label \%\PH{\ell} \nl} \\
  & \llvm{\PH{\ell_2} : \PH{\trad{i.body, $\ell_1$}{\ListOf{\B{Inst}}}_L}}
\end{split}
\end{align*}

@@

\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|c|c|}
\hline
Example nº & 01 & 02 & 03 & 04\\
\hline
variables & \yes & \yes & \yes & \yes \\
constants & \no & \yes & \no & \no \\
op. input & \yes & \no & \yes & \no \\
op. output & \yes & \no & \yes & \no \\
\hline
\multicolumn{5}{|c|}{instructions} \\
\hline
block & \yes & \no & \yes & \yes\\
local var & \no & \no & \yes & \yes \\
identity & \no & \no & \yes & \no \\
becomes equal & \yes & \yes & \yes & \yes \\
operation call & \no & \no & \no & \no \\
condition & \yes & \no & \no & \no \\
case & \no & \no & \no & \no \\
assertion & \no & \no & \no & \no\\
sequence & \yes & \yes & \yes & \yes \\
while & \no & \no & \no & \yes \\
\hline
\multicolumn{5}{|c|}{expressions} \\
\hline
int lit & \yes & \yes & \yes & \yes \\
bool lit & \yes & \yes & \no & \yes \\
vars & \yes & \yes & \yes & \yes \\
loc. vars & \no & \no & \yes & \yes \\
const & \no & \yes & \no & \no \\ 
succ & \no & \yes & \no & \yes \\
pred & \no & \yes & \no & \yes \\
+ & \yes & \no & \no & \yes \\
- & \yes & \no & \no & \no\\
\hline
\multicolumn{5}{|c|}{formulas} \\
\hline
and & \no & \no & \no & \no \\
or & \no & \no & \no & \no \\
not & \no & \no & \no & \no \\
$<$ & \yes & \yes & \no & \no\\
\hline
\end{tabular}
\end{center}
